A comprehensive approach to analyzing environmental data with non-detects

### 2024-09-03 Rmarkdown/paper.Rmd
new references

The same strategy can be incorporated into more complex models: here, we use a dataset of metals concentrations in municipal biosolids to demonstrate fitting a smoothing spline, a popular method for characterizing environmental time series [@simpson_modelling_2018; @murphy_generalized_2019; @beck_multiscale_2022]. It was fitted using *bgamcar1* [@bgamcar1], an extension of *brms* that accommodates continuous-time autoregression---accounting for the dependence of one observation on the previous one in unequally spaced time series [@trueman_comparing_2022; @simpson_modelling_2018]. Titanium concentrations at three wastewater treatment facilities (Sites 1--3) were modeled as follows:

>>>>

The same strategy can be incorporated into more complex models: here, we use a dataset of metals concentrations in municipal biosolids to demonstrate fitting a smoothing spline, a popular method for characterizing environmental time series and other problems [@simpson_modelling_2018; @murphy_generalized_2019; @beck_multiscale_2022; @chen_prediction_2020]. It was fitted using *bgamcar1* [@bgamcar1], an extension of *brms* that accommodates continuous-time autoregression---accounting for the dependence of one observation on the previous one in unequally spaced time series [@trueman_comparing_2022; @simpson_modelling_2018]. Titanium concentrations at three wastewater treatment facilities (Sites 1--3) were modeled as follows:
